---

---
<style>
@import url('https://fonts.googleapis.com/css?family=Scope+One&display=swap');
@import url('https://fonts.googleapis.com/css?family=Scope+One|Unica+One&display=swap&subset=latin-ext');
@import url('https://fonts.googleapis.com/css?family=Open+Sans&display=swap');

h1,h2 {font-family: 'Unica One', cursive;
  font-size: 25px;}
p2 {font-family: 'Unica One', cursive;
  font-size: 25px;}       
p {font-family: 'Open Sans', sans-serif;
  font-size: 15px;}   
</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
&nbsp;    


# Dynamic UI {.tabset .tabset-fade}  

## Intro to Dynamic UIs
&nbsp;  
<p>Using what you know about reactivity, learn how to make your UI dynamic! A dynamic UI is for when we want to add, remove or change the currently loaded widets based on the dynamic changes or user input. For instance: </p>
<ul>
<li><p>Display certain parts of the user interface if a certain condition is met </p></li>
<li><p>Display or hide aparts of the user interface when a certain condition is met</p></li>
<li><p>Modify the parameters of input control widgets.</p></li>
</ul>  

<p>**Let's go through these key UI changes in the tabs above.**</p>
<br>

<p2>Dynamic UI Example</p2>
<p>Still wondering what we're on about? Check out the following example and read through the subsequent code. The app displays a graph when a particular dataset is chosen:</p>

<center>
<iframe width="100%" height="475" src="https://g4most.shinyapps.io/dynamic_ex/" scrolling= "yes"></iframe>  
</center>  
<br>
```{r eval=FALSE, include=TRUE}
library(shiny)
library(datasets)

ui<-fluidPage(
  selectInput("data_input",label="Select data", 
              choices=c("mtcars","faithful","iris")), #dataset choices
  tableOutput("table_output"),
  uiOutput("ui")
)

server<-function(input,output) {
  getdata <- reactive({ get(input$data_input, 'package:datasets') })
  
  output$ui <- renderUI({
    #if the dataset is 'iris', display 'plot_output'
    if(input$data_input=="iris") plotOutput("plot_output",width="400px")
  })
  
  output$plot_output <- renderPlot({hist(getdata()[, 1])})
  output$table_output <- renderTable({head(getdata())})
}

shinyApp(ui = ui, server = server)

```


## Updating Inputs
&nbsp;  
in code add example of static vs. dynamic first  

add example of code + ui changing


## Dynamic Visibility
&nbsp;  
in code add example of static vs. dynamic first  

add example of code + ui changing


## Creating UI
&nbsp;  
in code add example of static vs. dynamic first  

add example of code + ui changing


## Checkpoint 5
&nbsp;  
