---

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
&nbsp;    
   

# Packages not to miss!  

The packages below have been developed by others for use in R Shiny. They allow for more interactivity without having learn another language (i.e., Python, Javascript, etc.). Depending on the developer, some packages are more flexible than others so I would recommend checking out the documentation to see the limits of each.  

&nbsp;  

### Plotly  

Plotly allows you to easily translate your ggplot2 graphics to an interactive web-based version, and also provides bindings to the plotly.js graphing library.  

[Plotly Website](https://plot.ly/r/)  

```{r plotly, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(plotly)
p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
            geom_bar(position = "dodge")
ggplotly(p)
```
&nbsp;  

## Dygraphs

Dygraphs provides rich facilities for charting time-series data in R and includes support for many interactive features including series/point highlighting, zooming, and panning.  

[Dygraphs Website](http://rstudio.github.io/dygraphs)  

```{r dygraph, echo=FALSE, message=FALSE, warning=FALSE}
library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
```
&nbsp;  

## Leaflet  

Leaflet is a JavaScript library for creating dynamic maps that support panning and zooming along with various annotations like markers, polygons, and popups.  

[Leftlet Github](http://rstudio.github.io/leaflet/)  

```{r}
library(leaflet)

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
m  # Print the map
```
&nbsp;  

## Datatables  

DataTables displays R matrices or data frames as interactive HTML tables that support filtering, pagination, and sorting.  

[DT Website](http://rstudio.github.io/DT/)  

```{r}
library(DT)
datatable(iris, options = list(pageLength = 5))
```
&nbsp;  

## visNEtwork  

Useful library to visualize networks  

[visNework Github](http://dataknowledge.github.io/visNetwork)  

```{r}
library(visNetwork)
nodes <- data.frame(id = 1:6, title = paste("node", 1:6), 
                    shape = c("dot", "square"),
                    size = 10:15, color = c("blue", "red"))
edges <- data.frame(from = 1:5, to = c(5, 4, 6, 3, 3))
visNetwork(nodes, edges) %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)
```
&nbsp;  

## d3heatmap  

Interactive heatmaps with D3 including support for row/column highlighting and zooming.  

[d3heatmap Website](https://github.com/rstudio/d3heatmap)  

```{r}
library(d3heatmap)
d3heatmap(mtcars, scale="column", colors="Blues")
```
&nbsp;  

## DiagrammeR  

A tool for creating diagrams and flowcharts using Graphviz and Mermaid. You can use this to create process flows.  

[DiagrammeR](http://rich-iannone.github.io/DiagrammeR/)  

```{r}
library(DiagrammeR)
grViz("
  digraph {
    layout = twopi
    node [shape = circle]
    A -> {B C D} 
  }")
```
&nbsp;  

## threejs  

threejs has produced widgets for R Shiny. If you want to play around with a 3-D movable graph.  

[threejs Website](https://github.com/bwlewis/rthreejs)  

```{r message=FALSE, warning=FALSE}
library(threejs)
z <- seq(-10, 10, 0.01)
x <- cos(z)
y <- sin(z)
scatterplot3js(x,y,z, color=rainbow(length(z)))
```




